Measuring Lattices

### 2023-05-22 C3/C3.tex
changes to make latex work :wq
Signed-off-by: larry andrews <larry6640995@gmail.com>
updating mostly Polar
uv5016 -- fix quote marks C3 -- replying to reviewers

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

\newcommand{\vdotv}[2]{${{\bf #1 \cdot #2}}$}
\newcommand{\Imaginary}[0]{$ \textfrak{I} $}
\newcommand{\Real}[0]{$ \textfrak{R} $}
\newcommand{\Exchange}[0]{$\textfrak{X}$}

@@

	\newcommand{\OPES}[0]{$E^3toS^6$}
	\newcommand{\OPESS}[0]{$$E^3toS^6$$}
	\newcommand{\MSVI}[0]{$M_{S^{6}}$}
	\newcommand{\MEIII}[0]{$M_{E^{3}}$}
	\newcommand{\Plus}[0]{$\textfrak{P}$}	
	\newcommand{\Minus}[0]{$\textfrak{M}$}

@@

	\begin{abstract}

		The Delone (Selling) scalars, which are used in 
		unit cell reduction and in lattice type determination,
		are studied in \CIII, the space of three complex variables.
		The three complex coordinate planes are composed of the six
		Delone scalars. The transformations at boundaries of the
		Selling reduced orthant are described as matrices of operators.
		A graphical representation as the projections onto the
		three coordinates is described.

@@

	We represent a vector 
	in \CIII{} by \{$(x_1,y_1)$, $(x_2,y_2)$, $(x_3, y_3)$\} 
	as an alternative to  \{(\si,\siv ), (\sii,\sv),(\sii,\svi)\}.

@@

	\begin{table}	
		\label{tab:operators}
		\caption{The Result column values give the products of each operator as applied to $(x_j, y_j)$}.
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
			$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

@@

	$\begin{bmatrix}
		\Minus{}_r		& 0					& 0 \\
		\Plus{}_r		&  \textrm{i}\Re{}	& \Re{} \\
		\textfrak{P}_r	& \textrm{i}\Im{}	& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0 				& 0 \\
		\Plus{}_r	&\textrm{i}\Im{}	& \Im{} \\
		\Plus{}_r	& \textrm{i}\Re{}	& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\label{thirdmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	&  \Re{}	& \textrm{i}\Re{} \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{} \\
		\Plus{}_r	&  \Re{}	&\textrm{i}\Re{} \\
	\end{bmatrix}$ \\

@@

	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	&  \textrm{i}\Re{}	& \Re{} \\
		\Plus{}_i	& \textrm{i}\Im{}	& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	& \textrm{i}\Im{}	& \Im{} \\
		\Plus{}_i	&  \textrm{i}\Re{}	& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0			& 0 \\
		\Plus{}_i	&  \Re{}	& \textrm{i}\Re{} \\
		\Plus{}_i	& \Im{}		& \textrm{i}\Im{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0		& 0 \\
		\Plus{}_i	& \Im{}	& \textrm{i}\Im{} \\
		\Plus{}_i	&  \Re{}& \textrm{i}\Re{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Re{}	& \Plus{}_r		& \Re{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Im{}	& \Plus{}_r		& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Im{}	& \Plus{}_r		&  \Im{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Re{}	& \Plus{}_r		& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Re{}	&\Plus{}_r		&   \textrm{i}\Re{} \\
		0		& \Minus{}_r	&  0 \\
		\Im{}	&\Plus{}_r		& \textrm{i}\Im{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Im{}	& \Plus{}_r	& \textrm{i}\Im{} \\
		0		&\Minus{}_r	&  0 \\
		\Re{}	& \Plus{}_r	&  \textrm{i}\Re{} \\
	\end{bmatrix}$ \\

	For the boundary at $s_5$: (the imaginary component of \cii{}).

	$\begin{bmatrix}
		\textrm{i}\Re{}	& \Plus{}_i		& \Re{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Im{}	& \Plus{}_i		& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Im{}	& \Plus{}_i		&  \Im{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Re{}	& \Plus{}_ri	& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Re{}	&\Plus{}_i		&   \textrm{i}\Re{} \\
		0		& \Minus{}_i	&  0 \\
		\Im{}	&\Plus{}_i		& \textrm{i}\Im{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Im{}	& \Plus{}_i	& \textrm{i}\Im{} \\
		0		&\Minus{}_i	&  0 \\
		\Re{}	& \Plus{}_i	&  \textrm{i}\Re{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Re{}	& \Re{}	& \Plus{}_r \\
		\textrm{i}\Im{}	& \Im{}	& \Plus{}_r  \\
		0				& 0		& \Minus{}_r  \\
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Im{}	&  \Im{}	& \Plus{}_r \\
		\textrm{i}\Re{}	& \Re{}		& \Plus{}_r \\
		0				& 0			& \Minus{}_r \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Re{}	&   \textrm{i}\Re{}	&\Plus{}_r \\
		\Im{}	& \textrm{i}\Im{}	&\Plus{}_r \\
		0 		&  0				& \Minus{}_r \\
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Im{}	& \textrm{i}\Im{}	& \Plus{}_r \\
		\Re{}	&  \textrm{i}\Re{}	& \Plus{}_r \\
		0		&  0				&\Minus{}_r \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Re{}	& \Re{}	& \Plus{}_i \\
		\textrm{i}\Im{}	& \Im{}	& \Plus{}_i \\
		0				& 0		& \Minus{}_i 
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Im{}	&  \Im{}	& \Plus{}_i \\
		\textrm{i}\Re{}	& \Re{}		& \Plus{}_i \\
		0				& 0			& \Minus{}_i \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Re{}	&   \textrm{i}\Re{} &\Plus{}_i \\
		\Im{}	& \textrm{i}\Im{}	&\Plus{}_i \\
		0		&  0				& \Minus{}_i \\
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Im{}	& \textrm{i}\Im{}	& \Plus{}_i \\
		\Re{}	&  \textrm{i}\Re{}	& \Plus{}_i \\
		0		&  0				&\Minus{}_i 
	\end{bmatrix}$ \\

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Re{} +\textrm{i}\Im{}	& $0$ \\
		$0$	& $0$						& \Re{} +\textrm{i}\Im{} \\
	\end{bmatrix}$ 
	$\bf{c}$.
	\\

@@

	\begin{center}
		$\begin{bmatrix}
			\Minus{}_r	& 0			& 0 \\
			\Plus{}_r	&  \Re{}	& \textrm{i}\Re{} \\
			\Plus{}_r	& \Im{}		&\textrm{i}\Im{}
		\end{bmatrix}	$
	\end{center}

@@

\begin{table}
	\begin{tabular}{l c c c c c c c c c}
		\toprule
		PDB id & Centering & a&b&c&$\alpha$&$\beta$&$\gamma$\\
		\midrule
	1DPY & R& 57.98& 57.98& 57.98& 92.02& 92.02& 92.02\\
	1FE5 & R& 57.98& 57.98& 57.98& 92.02& 92.02& 92.02\\
	1G0Z & H& 80.36& 80.36& 99.44& 90&    90&    120\\
	1G2X & C& 80.95& 80.57& 57.1 & 90&    90.35&  90\\
	1U4J & H& 80.36& 80.36& 99.44& 90&    90&    120\\
	2OSN & R& 57.10& 57.10& 57.10& 89.75& 89.75&  89.75\\
	\bottomrule
\end{tabular}	\\
\caption{Phospholipase A2 unit cells}
\label{PLA2}
\end{table}

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{2_06}
	\caption{The PLA2 unit cells Niggli-reduced. The similarity 
	of the 3 projections is indicative of the exact or nearly
exact rhombohedral symmetry.}
	\label{fig2}
\end{figure}
\begin{figure}
	\includegraphics[width=1.0\textwidth]{3_03}
	\caption{The PLA2 unit cells Delone-reduced. }
	\label{fig3}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\textwidth]{4_13}
	\caption{The PLA2 unit cells, Niggli-reduced, and five copies were perturbed 2\%
	orthogonally to \SVI{} vector. }
	\label{fig4}
\end{figure}

@@

@@

	The $C^{++}$ ~code for \CIII{} and related 
	software tools is available in github.com, in
	\url{https://github.com/duck10/LatticeRepLib.git}.

@@

	\bibliographystyle{iucrit}

>>>>

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

\newcommand{\vdotv}[2]{${{\bf #1 \cdot #2}}$}
\newcommand{\Imaginary}[0]{\mathcal{I}}
\newcommand{\Real}[0]{\mathcal{R}}
\newcommand{\Exchange}[0]{$\mathcal{X}$}

@@

	\newcommand{\OPES}[0]{$E^3toS^6$}
	\newcommand{\OPESS}[0]{$$E^3toS^6$$}
	\newcommand{\MSVI}[0]{$M_{S^{6}}$}
	\newcommand{\MEIII}[0]{$M_{E^{3}}$}
	\newcommand{\Plus}[0]{\mathcal{P}}	
	\newcommand{\Minus}[0]{\mathcal{M}}

@@

	\begin{abstract}
		The Delone (Selling) scalars, which are used in 
		unit cell reduction and in lattice type determination,
		are studied in \CIII, the space of three complex variables.
		The three complex coordinate planes are composed of the six
		Delone scalars. The transformations at boundaries of the
		Selling reduced orthant are described as matrices of operators.
		A graphical representation as the projections onto the
		three coordinates is described.

@@

	We represent a vector 
	in \CIII{} by \{$(x_1,y_1)$, $(x_2,y_2)$, $(x_3, y_3)$\} 
	as an alternative to  \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}.

@@

	\begin{table}	
		\label{tab:operators}
		\caption{The Result column values give the products of each operator as applied to $(x_j, y_j)$}.
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\mathcal{P}_r$ 	& $ \mathcal{P}_r(c_j)$ 	& $(x_j, x_j)$ 		& Plus real\\ 
			$\mathcal{P}_i$ 	&  $\mathcal{P}_i(c_j)$  	& $(y_j, y_j)$ 		& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ or $(x_j,0)$		& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ pr $(y_j,0)$ 		& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

	\citeasnoun{andrews2019b} listed the boundary transformations
	for each of the six \SVI{} boundaries. For each,
	they only listed 2 transformations, following \citeasnoun{Delaunay1932}
	and \citeasnoun{Delone1975}. That list is incomplete in the sense
	that applying the 24 reflections gives 24 boundary transformation,
	four for each boundary, rather than 12.

@@

	$\begin{bmatrix}
		\Minus{}_r		& 0					& 0 \\
		\Plus{}_r		&  \textrm{i}\Real{}	& \Real{} \\
		\mathcal{P}_r	& \textrm{i}\Imaginary{}	& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0 				& 0 \\
		\Plus{}_r	&\textrm{i}\Imaginary{}	& \Imaginary{} \\
		\Plus{}_r	& \textrm{i}\Real{}	& \Real{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\label{thirdmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
		\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{} \\
		\Plus{}_r	&  \Real{}	&\textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Real{} \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{} \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Imaginary{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0			& 0 \\
		\Plus{}_i	&  \Real{}	& \textrm{i}\Real{} \\
		\Plus{}_i	& \Imaginary{}		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0		& 0 \\
		\Plus{}_i	& \Imaginary{}	& \textrm{i}\Imaginary{} \\
		\Plus{}_i	&  \Real{}& \textrm{i}\Imaginary{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_r		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_r		&  \Imaginary{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
	\end{bmatrix}$ e
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_r		&   \textrm{i}\Real{} \\
		0		& \Minus{}_r	&  0 \\
		\Imaginary{}	&\Plus{}_r		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_r	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_r	&  0 \\
		\Real{}	& \Plus{}_r	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

	For the boundary at \sv: (the imaginary component of \cii{}).

	$\begin{bmatrix}
		\textrm{i}\Real{}	& \Plus{}_i		& \Real{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_i		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_i		&  \Imaginary{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_ri	& \Real{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_i		&   \textrm{i}\Real{} \\
		0		& \Minus{}_i	&  0 \\
		\Imaginary{}	&\Plus{}_i		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_i	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_i	&  0 \\
		\Real{}	& \Plus{}_i	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Real{}	& \Real{}	& \Plus{}_r \\
		\textrm{i}\Imaginary{}	& \Imaginary{}	& \Plus{}_r  \\
		0				& 0		& \Minus{}_r  \\
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	&  \Imaginary{}	& \Plus{}_r \\
		\textrm{i}\Real{}	& \Real{}		& \Plus{}_r \\
		0				& 0			& \Minus{}_r \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Real{}	&   \textrm{i}\Real{}	&\Plus{}_r \\
		\Imaginary{}	& \textrm{i}\Imaginary{}	&\Plus{}_r \\
		0 		&  0				& \Minus{}_r \\
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \textrm{i}\Imaginary{}	& \Plus{}_r \\
		\Real{}	&  \textrm{i}\Real{}	& \Plus{}_r \\
		0		&  0				&\Minus{}_r \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Real{}	& \Real{}	& \Plus{}_i \\
		\textrm{i}\Imaginary{}	& \Imaginary{}	& \Plus{}_i \\
		0				& 0		& \Minus{}_i 
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	&  \Imaginary{}	& \Plus{}_i \\
		\textrm{i}\Real{}	& \Real{}		& \Plus{}_i \\
		0				& 0			& \Minus{}_i \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Real{}	&   \textrm{i}\Real{} &\Plus{}_i \\
		\Imaginary{}	& \textrm{i}\Imaginary{}	&\Plus{}_i \\
		0		&  0				& \Minus{}_i \\
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \textrm{i}\Imaginary{}	& \Plus{}_i \\
		\Real{}	&  \textrm{i}\Real{}	& \Plus{}_i \\
		0		&  0				&\Minus{}_i 
	\end{bmatrix}$ \\

\subsection{Derivation}

Consider the \SVI{} vector 	
	\{$(x_1,y_1)$, $(x_2,y_2)$, $(x_3, y_3)$\};
in \CIII{} that vector is:  \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}.
Stated in \CIII{}, the problem is to find a matrix that converts a \CIII{}
vector to a more reduced one. Take the case of \si positive and the
other scalars negative.\\

 \{(-\si,~\siv-\si ),~(\siii+\si,~\sii+\si), (\svi+\si,~\sv+\si)\}\\
 =
\begin{tabular}{ccc}
	 $\begin{bmatrix}
 	~\\~\\~\\
 \end{bmatrix}$

$ \begin{Bmatrix}
 $(\si,\siv )$\\ $(\sii,\sv)$\\$(\siii,\svi)$
\end{Bmatrix}$
\end{tabular}\\

Here, one of the four possible result vectors has been chosen 
(arbitrarily).

Element 1 of result vector is (-\si,~\siv-\si ), and
it is created by multiplying the beginning \CIII{} vector by the
first row of the transformation matrix. In this case, we see
that \ci of the result only contains scalars from \ci of
the input, so the first row must contain some operator to
be multiplied times input \ci, and the second and third
elements of the matrix row must be zero. We create an operator
($Minus~real$) to transform the input \ci to the output \ci; so
the first row of the reduction matrix is: $\Minus{}_i	 0		 0$.

Element 2 of the result vector is (\siii+\si,~\sii+\si),
and
it is created by multiplying the beginning \CIII{} vector by the
second row of the transformation matrix. The result \cii
contains \si in both the real and imaginary parts. So
the first matrix element in that row must insert \si, the
real part of the input \ci, into both the real and imaginary
parts. An operator to produce that is created 
(Plus{}~real). Next we see that the result contains \sii and \siii.
\siii appears in the real part of the result element and in the
third part of the input vector. So the third element of the 
second matrix row must extract the \siii, the real part of 
\ciii of the input. So the second row now contains the Plus real
operator and the element to put the  real part of \ciii of the input.
The final matrix element of the second row (the second element)
must extract the real part of input \cii and place it in the
imaginary part of the output vector. The resulting second
row of the matrix is $\Plus_r~\Real~i\Real$.

Using similar logic, the third row of the matrix is:
$\Plus_r~\Imaginary~i\Imaginary$.

Having derived the first matrix, the other 23 can
be derived by the same process. However because all the
\SVI boundaries are related by the 24 reflection, the
other 23 matrices can be generated simply
by multiplying by each of the reflection matrices.

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Real{} +\textrm{i}\Imaginary{}	& $0$ \\
		$0$	& $0$						& \Real{} +\textrm{i}\Imaginary{} \\
	\end{bmatrix}$ 
	$\bf{c}$.
	\\

@@

	\begin{center}
		$\begin{bmatrix}
			\Minus{}_r	& 0			& 0 \\
			\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
			\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
		\end{bmatrix}	$
	\end{center}

@@

	\begin{table}
		\begin{tabular}{m{0.08\textwidth} c c c c c c c c c}
			\toprule
			PDB id & Centering & a&b&c&$\alpha$&$\beta$&$\gamma$\\
			\midrule
			1DPY & hR& 57.98& 57.98& 57.98& 92.02& 92.02& 92.02\\
			~~\& 1FE5 \\
			1G0Z  & hP& 80.36& 80.36& 99.44& 90&    90&    120\\
			~~\& 1U4J\\
			1G2X & mC& 80.95& 80.57& 57.1 & 90&    90.35&  90\\
			2OSN & hR& 57.10& 57.10& 57.10& 89.75& 89.75&  89.75\\
			\bottomrule
		\end{tabular}	\\
		\caption{Phospholipase A2 unit cells}
		\label{PLA2}
	\end{table}

@@

	\begin{figure}
		\includegraphics[width=1.0\textwidth]{2_06}
		\caption{The PLA2 unit cells Niggli-reduced. The similarity 
			of the 3 projections is indicative of the exact or nearly
			exact rhombohedral symmetry.}
		\label{fig2}
	\end{figure}

@@

	\begin{figure}
		\includegraphics[width=1.0\textwidth]{3_03}
		\caption{The PLA2 unit cells Delone-reduced. }
		\label{fig3}
	\end{figure}

	\begin{figure}
		\includegraphics[width=1.0\textwidth]{5_38}
		\label{5_38}
		\caption{The PLA2 cells Delone reduced and
		5 copies perturbed by 10\%.}
	\end{figure}

	\begin{figure}
		\includegraphics[width=1.0\textwidth]{6_53}
		\label{6_53}
		\caption{The same cells as plotted in Figure \ref{5_38} 
			and Delone reduced.}
	\end{figure}

\begin{figure}
	\includegraphics[width=1.0\textwidth]{7_14}
	\label{7_14}
		\caption{The same cells as plotted in Figure \ref{5_38} 
	and Delone reduced, and then each multiplied by the 24
	\SVI{} reflections.}
\end{figure}

@@

	The $C^{++}$ ~code for \CIII{} and related 
	software tools is available in github.com, in
	\url{https://github.com/duck10/LatticeRepLib.git}.
	The program CmdToC3 uses the required files.

@@

	\bibliographystyle{iucr}

### 2023-05-22 MeasuringLattices_uv5016/MeasuringLattices.tex
uv5016 -- fix quote marks C3 -- replying to reviewers

	"Measuring Lattices" is intended to be a summary of an invited talk
	for satellite meeting, "Mathematics and Computer Science for Materials Innovation: Crystal Lattice Classifications" of August, 2022, ECM33
	meeting (https://www.ecm33.fr/). The intent is describe in brief
	the basics of implementing a metric space that creates
	a measure of the "distances" between lattices.

@@

Crystallographic software delivered with diffractometers, used for processing
beamline data, etc. has produced more than one and quarter million structures. The structures have had internally consistent lattice and
symmetry identification, but there have been serious omissions in 
providing globally consistent lattice and symmetry identification
because of structures being done in the incorrect space group.
\citeasnoun{LeTrong2007} published the case of phospholipase
A2, and more were found in \citeasnoun{McGill2014}.
Not having failed to be observed is quite different from always working. Two regions of the space of lattice determination come into play here. 
First, how much error do we want to consider? For protein work, especially for serial crystallography, the errors can be large. Second, the simple methods commonly used in 
diffractometer software are likely to fail for 
some of the less common cases: centered lattices commonly cause interesting issues; lattices that are needle- or pancake-shaped are often challenging;
the five-fold ambiguity cited by \citeasnoun{Gruber1973} also causes confusion. The cited five-fold ambiguity is only for the particular
case that Gruber listed, but interchanges of the axes to produce
other, Buerger-reduced cells.

>>>>

	``Measuring Lattices'' is intended to be a summary of an invited talk
	for satellite meeting, ``Mathematics and Computer Science for Materials Innovation: Crystal Lattice Classifications'' of August, 2022, ECM33
	meeting (https://www.ecm33.fr/). The intent is describe in brief
	the basics of implementing a metric space that creates
	a measure of the ``distances'' between lattices.

@@

Crystallographic software delivered with diffractometers, used for processing
beamline data, etc. has produced more than one and quarter million structures. The structures have had internally consistent lattice and
symmetry identification, but there have been serious omissions in 
providing globally consistent lattice and symmetry identification
because of structures being done in the incorrect space group.
\citeasnoun{LeTrong2007} published the case of phospholipase
A2, and more were found in \citeasnoun{McGill2014}.
Not having failed to be observed is quite different from always working. Two regions of the space of lattice determination come into play here. 
First, how much error do we want to consider? For protein work, especially for serial crystallography, the errors can be large. Second, the simple methods commonly used in 
diffractometer software are likely to fail for 
some of the less common cases: centered lattices commonly cause interesting issues; lattices that are needle- or pancake-shaped are often challenging;
the five-fold ambiguity cited by \citeasnoun{Gruber1973} also causes confusion. The cited five-fold ambiguity is only for the particular
case that Gruber listed, but interchanges of the axes produce
other, Buerger-reduced cells.
